% !TEX TS-program = xelatex

% \documentclass[a6paper]{mikescards}
\documentclass[]{mikescards}

\usepackage{blindtext}
\usepackage{parcolumns}
\usepackage{mathtools}
% \usepackage{minipage}
% \usepackage{enumitem}

\begin{document}
\begin{recipe}{Classic Baguettes}{24-26m bake, 19h prep}{King Arthur Baking}

\begin{parcolumns}[colwidths={1=100pt}, rulebetween]{2}
  \colchunk{
    \begin{enumerate}
      \item \textbf{STARTER:}
      \item 113g Water, Cool
      \item $\frac{1}{16}$ tsp instant yeast*
      \item 120g AP Flour
      \item *sub: 25g sourdough starter
      \item 
      \item
      \item \textbf{DOUGH:}
      \item 1 $\frac{1}{2}$ tsp yeast
      \item 225g Water, lukewarm
      \item All the Starter
      \item 420g AP Flour
      \item 12g Salt
    \end{enumerate}
  }
  \colchunk{
    \begin{enumerate}
      \item \textbf{Starter}
      \item Mix all of the \textbf{STARTER} ingredients.
      \item Cover and Rest at Room Temp, \textbf{14h}.
      \item 
      \item \textbf{Dough}
      \item Mix everything together into soft, smooth dough:
      \item \hspace{10pt}Stand Mixer: 4 min, med-low speed.
      \item In lightly greased bowl, Cover and Rest: \textbf{45m}.
      \item Gently deflate, fold edges to center, turn over and return to bowl.
      \item Cover and Rest: \textbf{45m}.
      \item Turn out to lightly greased surface.
      \item Deflate, divide to thirds, round each.
      \item Cover and Rest: \textbf{15-60m}.
      \item Flatten and elongate each piece:
      \item \hspace{10pt}Fold almost in half, press seam w/ palm, rotate 180\textdegree, repeat \textbf{4x}. 
      \item Seam down, cup fingers and roll into 16" logs. Taper each end to point.
      \item Place seam down in couche folds. Let Rise \textbf{45m}.
      \item Preheat Oven to \textbf{450$\textdegree$F} with a cast iron pan, and boil 1 $\frac{1}{2}$ cup Water.
      \item Slice with Lame at 45\textdegree angle, 3-5 times.
      \item Bake on stone or sheet, \textbf{24-28m}. Add water to cast iron at start. 
      \item Remove and cool, or turn off oven and crack till cool.
    \end{enumerate}
  }
\end{parcolumns}



\end{recipe}
\end{document}
