% !TEX TS-program = xelatex

% \documentclass[a6paper]{mikescards}
\documentclass[]{mikescards}

\usepackage{blindtext}
\usepackage{parcolumns}
\usepackage{mathtools}
% \usepackage{minipage}
% \usepackage{enumitem}

\begin{document}
\begin{recipe}{David's Meatballs}{~30 min?}{Discord David}

\begin{parcolumns}[colwidths={1=120pt}, rulebetween]{2}
  \colchunk{
    \begin{enumerate}
      \item \textbf{BALLS}
      \item 1 lb ground meat
      \item $\frac{1}{2}$ cup bread crumbs
      \item 1 egg
      \item 5 clove garlic
      \item splash of milk or half-and-half
      \item 2 TBSP of meatball spice mix
      \item 2 tsp kosher salt
      \item medium-sized onion, minced
      \item \textbf{SPICE OPTION A:}
      \item baharat
      \item \textbf{SPICE OPTION B: David's}
      \item allspice, coriander, cumin, cinnamon, pepper, paprika
      \item \textbf{RICE}
      \item olive oil or butter
      \item 1 cup rice
      \item 2 cup chicken broth/stock
      \item (optional: $\frac{1}{4}$ cup vermicelli)
    \end{enumerate}
  }
  \colchunk{
    \begin{enumerate}
      \item \textbf{BALLS}
      \item Mix bread, salt, spices, milk, egg. Let sit \textbf{a few mins}.
      \item Mix into meat w/ garlic, $\frac{1}{2}$ onion. Let sit in fridge \textbf{a few hour}.
      \item 
      \item \textbf{COOK}
      \item Form \textbf{balls} w/ wet hands, sear on sides in OO in big pan.
      \item Remove \textbf{balls} from pan.
      \item Saute remaining onion for a bit.
      \item Add rice (and vermicelli). Cook, \textbf{med}, till rice opaque.
      \item Add any additional spice (maybe turmeric), toast \textbf{a few sec}.
      \item Add stock.
      \item Bring to a boil, then add salt to taste.
      \item Nestle \textbf{balls} in boiling rice. Cover, simmering \textbf{low}, \textbf{20min}.
      \item
      \item Load/Empty Dishwasher, generally cleaning the spaces. 
      \item 
      \item \textbf{Serve} with a veggie, and maybe some bread
    \end{enumerate}
  }
\end{parcolumns}



\end{recipe}
\end{document}