% !TEX TS-program = xelatex

% \documentclass[a6paper]{mikescards}
\documentclass[]{mikescards}

\usepackage{blindtext}
\usepackage{parcolumns}

\usepackage{fontspec}
\setmainfont[Ligatures=TeX]{Comic Neue}
\setsansfont[Ligatures=TeX]{Comic Neue}

\begin{document}
\begin{recipe}{Ginger Streusel Muffins}{30 min}{Fun City Discord}
\begin{parcolumns}[colwidths={1=120pt}, rulebetween]{2}
  \colchunk{
    \begin{enumerate}
      \item \textbf{Streusel}
      \item 1/2 C AP Flour
      \item 1/4 C Oats
      \item 1/4 C Granulated Sugar
      \item 1/4 tsp Salt
      \item 4 TBSP butter, room temp
      \item Chopped peanuts, Cinnamon
      \item \textbf{Muffins}
      \item 8 TBSP butter, room temp
      \item 3/2 C sugar (brown \& granul)
      \item 2 eggs, room temp
      \item 1 TBSP vanilla
      \item 2 C AP Flour
      \item 1 tsp kosher salt
      \item 2 tsp baking powder
      \item 1/4 C milk, room temp
      \item 1/2 C yogurt, room temp
      \item 16+ Oz Blueberries, smushed
      \item 1 tsp lemon zest 
      \item Smattering of ground ginger
      \item 1/2 tsp cinnamon
    \end{enumerate}
  }
  \colchunk{
    \begin{enumerate}
      \item \textbf{Streusel}
      \item Mix dry bits together.
      \item Cut in the butter in little chunks, 0.5 TBSP.
      \item \textbf{Muffins}
      \item Cream butter \& sugar. Add lemon, eggs. Add vanilla, yogurt.
      \item Sift dry stuff together.
      \item Mix dry into wets; bit of flour, bit of milk, back and forth.
      \item Put a bit of batter w/o berries into each cup.
      \item Fold in crushed berries.
      \item Fold in whole berries.
      \item Divvy it all out.
      \item Top with Streusel.
      \item 
      \item \textbf{BAKE:}
      \item \hspace{5pt} \textbullet \hspace{2pt} cupcake-size tin:     \textbf{5 min @ 425\textdegree} then \textbf{15min @ 350\textdegree}.
      \item \hspace{5pt} \textbullet \hspace{2pt} full-size muffin tin: \textbf{5 min @ 425\textdegree} then \textbf{20min @ 350\textdegree}.
      \item \hspace{5pt} \textbullet \hspace{2pt} ramekins also work well.
    \end{enumerate}
  }
\end{parcolumns}

\end{recipe}
\end{document}
