% !TEX program = xelatex

\documentclass[a6paper,landscape]{article}
% \usepackage[utf8]{inputenc} % this is needed for umlauts
% \usepackage[ngerman]{babel} % this is needed for umlauts
% \usepackage[T1]{fontenc}    % this is needed for correct output of umlauts in pdf
\usepackage{siunitx}
\usepackage[nonumber]{cuisine}
\usepackage{microtype}
\usepackage{fontspec}

\setmainfont[Ligatures=TeX]{Comic Neue}
\setsansfont[Ligatures=TeX]{Comic Neue}

% \usepackage[margin=0.0cm, layoutwidth=6in, layoutheight=4in]{geometry}
\usepackage[a6paper, landscape, margin=0.0cm]{geometry}
% Total | number of servings | step number | ingredient | quantity | units
\RecipeWidths{146mm}{10em}{.25em}{8.5em}{3em}{2em}
\renewcommand*{\recipetitlefont}{\large}

\begin{document}
% \renewcommand*{\recipefont}{\sffamily}
\begin{recipe}{Loco Moco (New York Times)}{4 Portions, 45 minutes}{}
  \freeform This classic Hawaiian dish is a ground beef patty above a pile of white rice, smothered with caramelized onion gravy and topped with a fried egg.
  \ing{1 lb}{ground beef/turkey}
  \ing[\fr14]{}{onion, chopped} 
  \ing[3]{}{garlic cloves}
  \ing[1 \fr1/2]{tsp}{W13e Sauce}
  % \ing[1]{tsp}{S\&P}
  In large bowl, combine ingredients. Mix until just combined. Form into four patties about \fr12-inch thick. Place the patties on a plate, cover, and transfer to the refrigerator for 20 minutes.
  \ing[1]{tbsp}{neutral oil}
  \ing[\fr34]{}{onion, sliced}
  Heat oil in large skillet over medium. Add onion and sauté until almost translucent. Reduce heat to low and continue until caramelized. Transfer to a bowl. 
  \ing[1]{tbsp}{neutral oil}
  Heat @ medium. Gently place the patties in the pan. Cook until browned, \textasciitilde4 min/side. Transfer patties to a clean plate.
  \ing[8]{oz}{mushrooms, sliced}
  \ing[2]{cup}{beef broth}
  \ing[1 \fr1/2]{tsp}{W13e Sauce}
  \ing[2]{tsp}{soy sauce}
  Heat @ medium, +oil if needed. Add mushrooms, and sauté until tender. Add S\&P, caramelized onions, broth, soy sauce, and W13e sauce. Simmer @ medium-low.
  \ing[2]{tbsp} {cornstarch}
  Whisk cornstarch w/ 2 tbsp of the broth until smooth. Stir into skillet, simmer until thickened. \textasciitilde5 min.
  \ing[4]{cups}{steamed white rice}
  \ing[4]{}{large eggs, fried}
  \ing[2]{}{chopped scallions}
  Place 1 cup steamed rice on each plate and top each serving with one patty, then the gravy, a fried egg and chopped scallions.

  % \freeform\hrulefill
  \end{recipe}

\end{document}